---
title: "Coronavirus Tweet"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
runtime: shiny
  
---

```{r setup, include=FALSE}
library(flexdashboard)
library(dplyr)
library(tidyr)
library(tidytext)
library(readr)
##didn't use it here, this was used in the dataprocessing.Rmd
#library(vsp)
#link:https://github.com/RoheLab/vsp
library(wordcloud2)
library(shiny)
library(purrr)
library(stringr)
library(ggplot2)
#layout all plot at once
library(gridExtra)
#reorder
library(forcats)
#cssholder
library(shinycssloaders)
library(plotly)
library(shinyWidgets)
#read data
wordfreq_bydateflo_top15_wocoron<-readRDS("wordfreq_bydateflo_top15_wocoron.rds")
#topiclswithlink<-readRDS("topiclswithlink.rds")
topiclswithlink<-readRDS("topiclsbyflowithlink.rds")
tidypredcovds<-readRDS("tidypredcovds.rds")
lmformds<-readRDS("lmformds.rds")
wordpredictors<-readRDS("wordpredictors.rds")
glmls<-readRDS("glmls.rds")
#sentifment ds
uncombineds<-readRDS("uncombineds.rds")
flockchoices<-tibble(flock=c("liberals","conservatives","media","issue-centric","pop culture","academia"))
topicchoices<-tibble(topic=c("topic 1","topic 2","topic 3",
                   "topic 4","topic 5", "topic 6","topic 7",
                   "topic 8", "topic 9","topic 10",
                   "topic 11","topic 12","topic 13",
                   "topic 14","topic 15","topic 16","topic 17",
                   "topic 18","topic 19","topic 20",
                   "topic 21","topic 22","topic 23",
                   "topic 24","topic 25","topic 26","topic 27",
                   "topic 28","topic 29","topic 30"))
casetypes<-c("total_confirm","total_test","confirm_test","new_cases","new_deaths","total_deaths")

```


Sidebar {.sidebar}
=================================================================
### Choose a date you want to see (data available from 02/01 to 03/31)

```{r}
#usually i put input widgets here
dateInput('date',
      label = 'Date input:',
      value = '2020-02-01'
)

checkboxGroupInput("flock", label = 'flock of interest', 
                 choices = list("liberals"="liberals", "conservatives"="conservatives", "media"="media",
                                "issue-centric"="issue-centric","pop culture"="pop culture","academia"="academia"),
                 selected=c("liberals","media","academia")
)

selectInput("topic", label = "Topic cluster (tweet wall)",
              choices = topicchoices$topic, 
               selected = "topic 1")


selectInput("oneflock", label = 'Choose one flock (tweet wall)',
             choices = flockchoices$flock)

#also, will put reactive data here
wordOfDate<-reactive({
  index<-str_c(as.character(input$date),"-","all")
  wordfreq_bydateflo_top15_wocoron[[index]]
})

wordOfFlock<-reactive({
  flockchoice<-input$flock
  datechoice<-as.character(input$date)
  indexls<-lapply(flockchoice, function(x){
    str_c(datechoice,"-",x)
  })
  index<-unlist(indexls)
  interestls<-wordfreq_bydateflo_top15_wocoron[index]
})

tweetsurl<-reactive({
  topchoice<-as.character(input$topic)
  flockchoice<-as.character(input$oneflock)
  #datechoice<-as.character(input$date)
  #indexdatflo<-str_c(datechoice,"-",flockchoice)
  tweetdf<-topiclswithlink[[flockchoice]][[topchoice]]
  tibble(embeded = tweetdf$embed_url%>%unlist())
})

glmsum<-reactive({
  flockchoice<-as.character(input$oneflock)
  return(glmls[[flockchoice]])
})
#for each chunck below, i just put renderXXX functions, eg. renderwordcloud, renderplot, renderUI...
```

It is said that social network is a place where people discuss things they care about, regarding public health, politics, economics, and etc.  

Often, the discussions are correlated with the development of an event, and can even predict the result, such as an election. During last H1N1 outbreak, there are people using twitter to see 
if the amount of disease-related words can predict the spread of H1N1. Therefore, for the COVID-19 outbreak, we are interested in examining if such relationship exists. As a biginning, we'll look at the linear relationship. 

The app serves to allow users to explore the tweets under #coronavirus, and plot the relationships between COVID-19 cases and tweet words. 

Tweet Explore
=================================================================

Row{data-height=650}
-----------------------------------------------------------------------
### Word Frequency (Summary by flock within the date)**words occur in > 40 days: epidemic, infected, outbreak, pandemic, quarantine, realdonaldtrump, wuhan

```{r}
renderPlot({
  ls = wordOfFlock()
  ##plot all dataframe in the chosen list
  plot.list = lapply(seq_along(ls), function(i) {
    dfname = names(ls)[i]
    df = ls[[i]] %>% mutate(word = fct_reorder(word, n))
    ggplot(df, aes(y=word)) +
    theme_bw() +
    geom_bar(aes(weight = n),fill ="skyblue", width = .7)+
      labs(title=dfname)+
      theme(text=element_text(size=17))
  })
  # Lay out all the plots together
  n <- length(plot.list)
  if(n >= 1){
    nRow <- floor(sqrt(n))
    do.call("grid.arrange", c(plot.list, nrow=nRow))
  }
})
```

Row{data-height=350}
-----------------------------------------------------------------------

### Word Frequency (Summary of the date-word cloud) 
```{r}
renderWordcloud2(
  wordcloud2(wordOfDate(), size = 0.5, color = 'random-dark')
)
```

### Sentiment distribution of each flock 
```{r}
#filter by day and flock chosen
sents<-reactive({
  d<-as.character(input$date)
  fl<-input$flock
  dayds<-uncombineds%>%filter(str_detect(column_label,d))
  flockds<-dayds%>%filter(str_detect(column_label,fl))
})

#plot sentiment
renderPlot({
  ds<-sents()
  ds%>%ggplot(aes(x=column_label,y=sentiment))+geom_boxplot()+theme_bw()
})
```

Tweet Wall (Topic clusters)
=================================================================
Column{data-width=400}
-----------------------------------------------------------------------

```{r}
fillRow(
  uiOutput("twitter"),
  verbatimTextOutput("glmsummary")  
)
output$twitter<-
  renderUI({
    tags$head(
    tags$script("!function(d,s,id){var js,fjs=d.getElementsByTagName(s)    [0],p=/^http:c(/.test(d.location)?'http':'https';if(!d.getElementById(id)){js=d.createElement(s);js.id=id;js.src=p+'://platform.twitter.com/widgets.js';fjs.parentNode.insertBefore(js,fjs);}}(document,'script','twitter-wjs');")
  )
    df = tweetsurl()
    urlvec<-df$embeded
    urlvec%>% HTML()
})
output$glmsummary<-
  renderPrint({
    print(glmsum())
  })
```


Spread of Covid-19 versus Tweets
=================================================================
Row{data-height=400}
-----------------------------------------------------------------------
### Covid-19 Confirmed, Tested
```{r}
## Data source: https://covid.ourworldindata.org/data/ecdc/full_data.csv
renderPlot({
  ds<-tidypredcovds%>%filter(case_type==c("total_confirm","total_test"))
  ggplot(ds,aes(x=date, y=case_number,group=case_type))+geom_line(aes(color=case_type))+theme_bw()
})


```

### Covid-19 Confirm per 100 tests
```{r}
renderPlot({
  ds<-tidypredcovds%>%filter(case_type=="confirm_test")
  ggplot(ds,aes(x=date, y=case_number))+geom_line()+theme_bw()
})
```


Row{data-height=600}
-----------------------------------------------------------------------
### Facet plot - relationship between a chosen word's occurance and log(case numbers) 
```{r}
#common words: words occur in more than 40 days
selectInput("word", label = "Top Common Words",
              choices = wordpredictors, 
               selected = "epidemic")

wordtofacet<-reactive({
  wordpred<-input$word
  tidypredcovds%>%filter(word==wordpred)
})

renderPlot({
  df<-wordtofacet()
  df%>%ggplot(aes(x=n, y=log(case_number)))+geom_point()+facet_wrap(~case_type,scales = "free")+labs(x="count",y="log(case number)")+theme_bw()
},height=370)
```

### Single plot - plot the word and case-type of interest (w/o taking log)
```{r}

#common words: words occur in more than 40 days
selectInput("word2", label = "Top Common Words (x)",
              choices = wordpredictors, 
               selected = "infected")
#common words: words occur in more than 40 days
selectInput("casetype", label = "Case Type (y)",
              choices = casetypes, 
               selected = "total_confirm")


interestds<-reactive({
  wordpred<-input$word2
  case<-input$casetype
  tidypredcovds%>%filter(word==wordpred)%>%filter(case_type==case)
})

renderPlotly({
  df<-interestds()
  plot_ly(
    type = 'scatter',
    x= df$n,
    y= df$case_number,
    text=paste("Date: ",df$date,
               "<br>Word Count: ",df$n,
               "<br>Case Nmuber: ",df$case_number),
    hoverinfo='text',
    height = 330
  )
})
```

### Linear model(take log for total confirm & test)
```{r}
checkboxGroupInput("wordpreds", label = 'Choose one or more words as predictors', 
                 choices = wordpredictors,selected = "wuhan"
)

radioButtons("depend", label = 'Choose a case-type as the dependent variable',
             choices = casetypes, selected = "total_confirm")

#change to original lmformds
#select the columns user choose
#do logtransformation for non-0 values
#cauclate lm
lmds<-reactive({
   preds<-input$wordpreds
   dep<-input$depend
   allsel<-c(preds,dep)
   ds<-lmformds[,allsel]
   cleands<-ds%>%drop_na()
   if(input$depend %in% c("total_confirm","total_test")){
     cleands[,dep]<-log(cleands[,dep])
     isinfin<-sapply(cleands,is.infinite)
     cleands[isinfin]<-0
   }else{
     #cleands
     cleands
   }
   lm(reformulate(input$wordpreds,input$depend),cleands)
 })
 
# renderTable(
#   lmds()
# )

renderPrint({
   summary(lmds())
})
```
